\sectionTitle{Projects}{\faLaptop}

\begin{projects}
	\project
	{Brain Cancer Segmentation and Classification}{ Apr. 2023 - Oct. 2023}
	{\github{davidebelcastro-sig/BrainCancerSegmentation-Classification} \website{https://makerfairerome.eu/it/espositori/?edition=2023&exhibit=2320497}{Maker Faire 2023}}
	{This project aims to use \textbf{Machine Learning} and \textbf{AI} to segment and classify brain tumors. 
	It includes a user-friendly \textbf{GUI} for uploading and visualizing images, leveraging various libraries for its
	implementation. The tool provides segmentation results, including tumor probability and area, and classifies 
	tumors into glioma, meningioma, or pituitary categories.}
	{Python, OpenCV, Scikit-Learn, TensorFlow, NumPy, Flet}
				
	\project
	{Jarvis}{Feb. 2023 - Sep. 2023}
	{\github{struggling-student/Jarvis}}
	{An \textbf{automated tool} developed using Python and Selenium, designed to answer questions on the Moodle platform. 
	The tool can identify and answer questions that it has previously encountered. If it encounters new questions during a 
	quiz, it has the capability to download and store them for future use. This ensures that over time, it becomes more 
	knowledgeable about the questions in the quizzes.}
	{Python, Selenium, OpenCV, Scikit-Learn, Pillow}

	\project
	{WASAPhoto}{Oct. 2022- Jan. 2023}
	{\github{struggling-student/WASAPhoto}}
	{Users can search for other profiles by username, interact with photos by 
	liking or commenting, and even have the capability to ban other users. The platform is robustly built with a Go
	\textbf{backend} for efficient server-side operations and a Vue.js \textbf{frontend} for a dynamic user interface.}
	{Git, OpenAPI, GoLang, VueJS, Docker}
\end{projects}