%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}


% Set applicant's personal data for header
\name{Lucian Dorin Crainic}
\address{Rome, Italy}
\webpage{luciancrainic.github.io}
\contacts{(+39) 3270499569\linebreak crainic.lucian@gmail.com}
\github{github.com/luciancrainic}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
\begin{cvsection}{About Me}
	Hello, I'm a Computer Science student at La Sapienza in Rome. My interests in Computer Science include different fields such as Data Science, Artificial Intelligence and Human Computer Interaction.

	I am a hardworking, responsible, trustworthy and ambitious student that really enjoys Computer Science. I am always ready to share my experience and learn from others. 
	
\end{cvsection}
\begin{cvsection}{Education}
		\begin{cvsubsection}{La Sapienza University}{Rome, Italy}{Sep 2020 -- May 2023 (Expected)}
			\begin{itemize}
				\item \textbf{B.S. in Computer Science}
				\item \textbf{Graduate Coursework:} Python, Discrete Math, Java, Computer Architecture, Algorithms, Algebra, Operating Systems, Databases, Computer Networks, Software Engineering, Web and Software Engineering.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{IIS Einstein-Bachelet}{Rome, Italy}{Sep 2015 -- Jun 2020}
			\begin{itemize}
				\item IT and Telecomunication High School diploma.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Experience}
		\begin{cvsubsection}{Small Business - AlbaSocial}{Rome, Italy}{2018 – 2020}
			%iChat AV			
			\begin{itemize}
            \item Driven and ambitious Founder of a social media agency dedicated to continous business improvement focused on enhancing revenue and stremlining business operations.
            \item Built a responsive website that allows a client to buy social media services for different platforms.
            \item Utilized the API of a service provider, and built an interactive, real-time shop to purchase different services.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Management - KBM Consultants}{London, UK}{21 March - 25 March 2019}	
			\begin{itemize}
            	\item Professional Resume writing and mentoring skills.
				\item Impact and uses of social media, creating leads and marketing it.
                \item Developing the data, product cycle.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Graphic Designer - Freelance}{Rome, Italy}{2016-2017}
			\begin{itemize}
            	\item Developed and implemented designs to existing and new product packaging. Developed Business collateral including sell sheets, catalogs, brochures, posters, advertisements, and web assets. Prepared and sent final artwork to vendos to produce.
            	\item Used HTML/CSS,JavaScript in creation and maintenance of personal portfolio website.
            	\item Started with Adobe Photoshop and then learned Adobe Illustrator.
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}

\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Advanced:} Python, GO, Java, HTML, CSS, JavaScript, Git, Unix, Vue.js, OpenAPI, MySQL
				\item \textbf{Familiar:} C, Modelica, SQLite
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{WASAPhoto - Academic}{}{}
			\begin{itemize}
            	\item Defined APIs using the OpenAPI standard.
            	\item Designed and developd the server side ("backend") in GO.
            	\item Designed and developed the client side ("frontend") in JavaScript.
            	\item Created a Docker container image for deployment.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{WikipediaWebScraper - Academic}{}{}
			\begin{itemize}
            	\item Developed a Wikipedia web scraper in Java with Selenium.
            	\item Designed and Developed a graphic interface in Java Swing.
			\end{itemize}
		\end{cvsubsection}


		\begin{cvsubsection}{Portfolio website - Personal}{}{}
			\begin{itemize}
            	\item Developed the frontend with HTML,CSS and Javascript.
            	\item Sharing of photography pictures that i shoot and book reviews.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
